Complete draft

### 2019-05-10 doc/point.tex
cleaned up version

The trace term is
\begin{align}
 \tr(\textbf{C}^{-1} \textbf{S}_\beta \textbf{C}^{-1} \textbf{C}_0) & \approx  \tr(\textbf{C}_0^{-1} \textbf{S}_\beta) \\
 & = \bar{N} \tr(\xi_{\delta\delta,\beta}) + \tr(\frac{1}{\sigma^2_v} \xi_{vv,\beta})\\
 & = \int n(x) \xi_{\delta \delta,\beta}(x,x) d^3x +  \sum_{i\in N_{gal}} \frac{1}{\sigma^2_{v,i}} \xi_{vv,\beta}(x_i,x_i)
\end{align}

The remaining term to the leading term in $\bar{N}$ is
\begin{align}
 \tr(\textbf{C}^{-1} \textbf{S}_\alpha \textbf{C}^{-1} \textbf{S}_\beta) & \approx  \tr(\textbf{C}_0^{-1} \textbf{S}_\alpha \textbf{C}_0^{-1} \textbf{S}_\beta)  \\
 & = \bar{N} \tr(\xi_{\delta v,\alpha} \frac{1}{\bm{\sigma}^2_v} \xi_{v\delta,\beta} ) + \tr(\frac{1}{\bm{\sigma}^2_v} \xi_{vv,\alpha}  \frac{1}{\bm{\sigma}^2_v}  \xi_{vv,\beta})\\
 & = \int n(x) \sum_{i\in N_{gal}} \xi_{\delta v,\alpha}(x,x_i) \frac{1}{\sigma^2_{v,i}} \xi_{v\delta,\beta} (x_i,x) d^3x \\
 & +  \sum_{i,j\in N_{gal}} \frac{1}{\sigma^2_{v,i}} \xi_{vv,\alpha}(x_i,x_j)  \frac{1}{\sigma^2_{v,j}}  \xi_{vv,\beta}(x_j,x_i).
\end{align}

@@

We evaluate $\textbf{x}^T \textbf{C}^{-1}\textbf{x}$ by splitting up the counts and velocities.  The data vector $\textbf{x}$ is composed of the counts
 $\textbf{N}-\bar{N}$ and peculiar velocities $\mathbf{\Delta v}$, whereas $\textbf{S}$ is comprised of $\bar{N}^2\xi_{\delta\delta}$, $\bar{N}\xi_{\delta v}$,
and $\xi_{vv}$.  In this manner
\begin{align}
\textbf{x}^T \textbf{C}_0^{-1}\textbf{S}\textbf{C}_0^{-1} \textbf{x}& = (\textbf{N}-\bar{N}) \xi_{\delta\delta}  (\textbf{N}-\bar{N})  + 2  (\textbf{N}-\bar{N}) \xi_{\delta v}\frac{\mathbf{\Delta v}}{\bm{\sigma}_v^2}+ 
\frac{\mathbf{\Delta v}}{\bm{\sigma}_v^2} \xi_{vv}\frac{\mathbf{\Delta v}}{\bm{\sigma}_v^2}.
\end{align}
Noting that $N_i=1$ when the cell $i$ contains a galaxy and zero otherwise and that only cells with a peculiar velocity measurement contribute ($\sigma_v =\infty$
for cells without such a measurement), and that in the limit of infinitely small cells, $\bar{N}\sum_{i,j\in N_{cell}} = n \int dV$, where $n$ is the galaxy number density,
\begin{align*}
\textbf{x}^T \textbf{C}_0^{-1}\textbf{S}\textbf{C}_0^{-1} \textbf{x}& = \sum_{i,j\in N_{gal}} \xi_{\delta\delta,ij} -2 \bar{N} \sum_{i\in N_{gal},j\in N_{cell}} \xi_{\delta\delta,ij}\\
& +\bar{N}^2  \sum_{i,j\in N_{cell}}  \xi_{\delta\delta,ij} + 2 \sum_{i,j\in N_{gal}} \frac{\Delta v_j}{\sigma_{v,j}^2} \xi_{\delta v,ij} \\
& -2\bar{N}\sum_{i\in N_{cell}, j\in N_{gal}} \frac{\Delta v_j}{\sigma_{v,j}^2} \xi_{\delta v,ij}  + \sum_{i,j\in N_{gal}} \frac{\Delta v_i}{\sigma_{v,i}^2} \xi_{vv,ij} \frac{\Delta v_j}{\sigma_{v,j}^2}\\
& = \sum_{i,j\in N_{gal}} \left( \xi_{\delta\delta,ij} + 2  \frac{\Delta v_j}{\sigma_{v,j}^2} \xi_{\delta v,ij} + \frac{\Delta v_i}{\sigma_{v,i}^2} \xi_{vv,ij} \frac{\Delta v_j}{\sigma_{v,j}^2}\right)\\
&-2 n \sum_{i\in N_{gal}}\int \left(\xi_{\delta\delta,iV} + \frac{\Delta v_i}{\sigma_{v,i}^2} \xi_{v \delta,iV}\right) dV\\
& +n^2  \int \xi_{\delta\delta,V_1V_2}dV_1dV_2.
\end{align*}

>>>>

The trace term depends on only the zero-lag correlation
\begin{align}
 \tr(\textbf{C}^{-1} \textbf{S}_\beta \textbf{C}^{-1} \textbf{C}_0) & \approx  \tr(\textbf{C}_0^{-1} \textbf{S}_\beta) \\
 & = \bar{N} \tr(\xi_{\delta\delta,\beta}) + \tr(\frac{1}{\sigma^2_v} \xi_{vv,\beta})\\
 & = \int n(x) \xi_{\delta \delta,\beta}(x,x) d^3x +  \sum_{i\in N_{gal}} \frac{1}{\sigma^2_{v,i}} \xi_{vv,\beta}(x_i,x_i).
\end{align}

The term in the Fisher matrix, to the leading term in $\bar{N}$ is
\begin{align}
 \tr(\textbf{C}^{-1} \textbf{S}_\alpha \textbf{C}^{-1} \textbf{S}_\beta) & \approx  \tr(\textbf{C}_0^{-1} \textbf{S}_\alpha \textbf{C}_0^{-1} \textbf{S}_\beta)  \\
 & = \bar{N}^2 \tr(\xi_{\delta \delta,\alpha}\xi_{\delta \delta,\beta})+
 \bar{N} \tr(\xi_{\delta v,\alpha} \frac{1}{\bm{\sigma}^2_v} \xi_{v\delta,\beta} ) + \tr(\frac{1}{\bm{\sigma}^2_v} \xi_{vv,\alpha}  \frac{1}{\bm{\sigma}^2_v}  \xi_{vv,\beta})\\
 & = \int n(x) n(y) \xi_{\delta \delta,\alpha}(x,y)\xi_{\delta \delta,\beta}(y,x) d^3x d^3y \\
 & + \int n(x) \sum_{i\in N_{gal}} \xi_{\delta v,\alpha}(x,x_i) \frac{1}{\sigma^2_{v,i}} \xi_{v\delta,\beta} (x_i,x) d^3x \\
 & +  \sum_{i,j\in N_{gal}} \frac{1}{\sigma^2_{v,i}} \xi_{vv,\alpha}(x_i,x_j)  \frac{1}{\sigma^2_{v,j}}  \xi_{vv,\beta}(x_j,x_i).
\end{align}

@@

We evaluate $\textbf{x}^T \textbf{C}^{-1}\textbf{x}$ by splitting up the counts and velocities.  The data vector $\textbf{x}$ is composed of the counts
 $\textbf{N}-\bar{N}$ and peculiar velocities $\mathbf{\Delta v}$, whereas $\textbf{S}$ is comprised of $\bar{N}^2\xi_{\delta\delta}$, $\bar{N}\xi_{\delta v}$,
and $\xi_{vv}$.  In this manner
\begin{align}
\textbf{x}^T \textbf{C}_0^{-1}\textbf{S}\textbf{C}_0^{-1} \textbf{x}& = (\textbf{N}-\bar{N}) \xi_{\delta\delta}  (\textbf{N}-\bar{N})  + 2  (\textbf{N}-\bar{N}) \xi_{\delta v}\frac{\mathbf{\Delta v}}{\bm{\sigma}_v^2}+ 
\frac{\mathbf{\Delta v}}{\bm{\sigma}_v^2} \xi_{vv}\frac{\mathbf{\Delta v}}{\bm{\sigma}_v^2}.
\end{align}
Noting that $N_i=1$ when the cell $i$ contains a galaxy and zero otherwise and that only cells with a peculiar velocity measurement contribute ($\sigma_v =\infty$
for cells without such a measurement), and that in the limit of infinitely small cells, $\bar{N}\sum_{i,j\in N_{cell}} = n \int dV$, where $n$ is the galaxy number density,
\begin{align*}
\textbf{x}^T \textbf{C}_0^{-1}\textbf{S}\textbf{C}_0^{-1} \textbf{x}& = \sum_{i,j\in N_{gal}} \xi_{\delta\delta,ij} -2 \bar{N} \sum_{i\in N_{gal},j\in N_{cell}} \xi_{\delta\delta,ij}\\
& +\bar{N}^2  \sum_{i,j\in N_{cell}}  \xi_{\delta\delta,ij} + 2 \sum_{i,j\in N_{gal}} \frac{\Delta v_j}{\sigma_{v,j}^2} \xi_{\delta v,ij} \\
& -2\bar{N}\sum_{i\in N_{cell}, j\in N_{gal}} \frac{\Delta v_j}{\sigma_{v,j}^2} \xi_{\delta v,ij}  + \sum_{i,j\in N_{gal}} \frac{\Delta v_i}{\sigma_{v,i}^2} \xi_{vv,ij} \frac{\Delta v_j}{\sigma_{v,j}^2}\\
& = \sum_{i,j\in N_{gal}} \left( \xi_{\delta\delta,ij} + 2  \frac{\Delta v_j}{\sigma_{v,j}^2} \xi_{\delta v,ij} + \frac{\Delta v_i}{\sigma_{v,i}^2} \xi_{vv,ij} \frac{\Delta v_j}{\sigma_{v,j}^2}\right)\\
&-2 n \sum_{i\in N_{gal}}\int \left(\xi_{\delta\delta,iV} + \frac{\Delta v_i}{\sigma_{v,i}^2} \xi_{v \delta,iV}\right) dV\\
& +n^2  \int \xi_{\delta\delta,V_1V_2}dV_1dV_2.
\end{align*}
\begin{comment}
